Community-Conditioned Language Models

### 2020-10-21 paper/paper.tex
analysis notes

 - Different communities have different levels of linguistic complexity
 - different language models are able to recognize such differences
 - level at which the community embedding is taken into account in the language model influences this.
 - community vectors are correlated with extra-linguistic information.
 - stability is correlated with language complexity

@@

 \section{Experimental setup}
 \section{Results and analysis}

- Computation of loss/community/model (show all)
- Computation of confusion matrix for community inference per model (eg. show only best and worst model) (on test set)
- Computation of H(c,m) entropy of community identification (on test set)
- Correlation between H(c,m) for various models. Identification of specific communities by hand
- Correlation between H(c,m) and Stability(c).

>>>>

\begin{enumerate}
\item Different communities have different levels of linguistic
  complexity
\item different language models are able to recognize such differences
\item level at which the community embedding is taken into account in the language model influences this.
\item community vectors are correlated with extra-linguistic information.
\item stability is correlated with language complexity
\end{enumerate}

@@

\section{Results and analysis}

% Computation of loss/community/model (show all)
\begin{table}
  \centering
  \begin{tabular}{ccc}
    todo &todo &todo 
  \end{tabular}
  \caption{Model losses per community}
  \label{tab:losses}
\end{table}
TODO commentary

TODO: say why we can't use the losses directly!
Turn a CCLM into a community classifier using Bayes theorem: The
probability that a given post $m$ belongs to a community $c_i$ can be
calculated as:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]

$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is our normalisation factor, which can be set so that
\[\sum_i P(c=c_i | m) = 1\].

Knowing that $m$ \emph{actually} comes from community $c_j$, we test
the recall and precision abilities of our classifier.  if we let
$C_{ij} = average_{m ∈ Posts(c_j)}(P(c=c_i | m))$ then $C$ is a
confusion matrix for it.

(TODO: on what set?)

TODO: show a few relevant matrices. (eg. show only best and worst model) and commentary.

TODO: why don't we use F scores or such bullshit?

TODO:Define \(D_j\) as the discrete probability distribution given by \(C_{ij}\) for fixed \(j\).

We then compute the perplexity of the classifier, per given community
$j$, as the exponential of the entropy of the distribution \(D_j\):

\[Ppl_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

\(Ppl_j\) is a measure of the capability (or inability) of the model
to correctly identify a message as coming from a certain
community. (ie. it aggregates confusion on a column of the matrix).

We can then analyse the correlation between \(Ppl^M_j\) for various models $M$.

- Correlation between H(c,m) for various models. Identification of specific communities by hand
- Correlation between H(c,m) and Stability(c).
